It's Never Too Late To Learn\\ \emph{Using Online Machine Learning in Distributed Systems}

### 2016-01-22 writeups/msr_workshop/paper.tex
notes on what to integrate/add

\title{
  It's Never Too Late To Learn\\
  \emph{Using Online Machine-Learning in Distributed Systems}
}
\author{}
\date{}

@@

@@

\section{Issues of ML in Systems}

Using online ML in distributed systems poses many issues and open questions.
Here are some preliminary questions that we think are worth studying:

@@

@@

@@

>>>>

\title{
  It's Never Too Late To Learn\\
  \emph{Using Online Machine Learning in Distributed Systems}
}
\author{}
\date{}

@@

- contextual multi-armed bandits. idea is to provide a context, get an action,
and only observe reward for that action. This matches the dist systems world well. It will generate new
policies using ML that we could not come up with by just thinking, and may not
even be able to describe. We argue in favor of opacity and rely instead on the guarantees
provided by the ML optimization.

We describe some of hte unkowns we face and where ML can come in

@@

\section{Applying Online Learning to Distributed Systems}

- Framework is to threat ML as a black box. The Decision Service is an exmaple of such a system.
The blackbox takes as input a context, teslls us an action, and then expects us to give it
a reward. Thus it can be placed anywher a decision has to be made, such as which request
to route to, where to place replicas, etc.. Despite the simplicity provided by the ML interface
and we assume the rest of it is solved: it colelcts the data, optimizes a model, and delivers the model
to us quickly (let's even assume the latency of htis loop, which can be minutes, is good enough to adapt
to the rate of change in our environment). Now the remaining piece is to figure out what
to enter as context, how to execut the actions, and how to determine or report rewards.

We argue that there are big challenges even in doing just these things...

Using online ML in distributed systems poses many issues and open questions.
Here are some preliminary questions that we think are worth studying:
- Questions viewed from the lens of characteristics of distributed systems

[merge below above]

@@

- Should feature vectors cut across the levels or not?
- In general should be composable if at each level can define decision and reward,
and exploration randomization is different at each level

@@

- quesiton of what features to include is there, but being conservative usually the right
way to go
- bigger quesiton is how ml component deals with omissions and other problems. Separate
into failure sections? Yeah, replace this with ``failures'' and move feature selection stuff
down to last section

@@

- Probably omit this, or replace with ``Randomization''. Basically, we already know
that exploratoin-exploitation is the right approach, and that will be encapsulated
by the ML component (its decisions will reflect this, and it will take care of
computing probabilities etc.). But there's an interesting point about inherent randomization
in systems

\section{Expanding the scope}

Two drawbacks: opacity and scope.

Opacity (also, which features matter?)
- We are also pursuing work on cracking models open to see what they are doing inside.
There are different ways to gain insight as to what a model is doing. For example a simple
linear model may learn a vector of weights on the supplied features. These weights can be
studied, and indeed some techniques such as lasso are oftne used to reduce the number of features. However, these
techniques need to be handled carefully. Just becasue a feature has 0 weight doesn't mean it
can be removed: perhaps it is unimportant preceisely because it exists, and its removal all of
asudden changes the weight on other features.

Scope:
The above replaces the policy behind a decision with one backed by an ML learning system.
Indeed systems like hte DS were designed to intervene at the decision making point in a
slim way. The above outlines the issues which tackled would result in ML based policies,
new ones. However, once the above has been mastered, there is the question of whether ML
can influence distributed systems design at a higher level. For example, can it suggest
different mechanisms for achieving a goal, or perhaps a different design of the system in the first place?
